### 2018-12-09 paper/paper.tex
Add more figures
Finished data preperation and dataset selection

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{sectsty}
\usepackage{multicol, caption}
\usepackage{graphicx}
\usepackage{wrapfig}
%\usepackage{biblatex}
\usepackage[margin=0.5in]{geometry} % don't know what size margins to use

\newenvironment{Figure}
  {\par\medskip\noindent\minipage{\linewidth}}
  {\endminipage\par\medskip}

@@

            In this paper we explore the selection public datasets, data preparation,
            feature extraction and finally the selection and tuning of classifiers.
            We will do this following the process illustrated in Figure \ref{fig:process}.
        \section{Dataset Selection}
            The correct selection of a dataset was crucial to the testing of 
            different types of features. There were many characteristics that were
            on our `wishlist.' Such as having the freedom of processing 
            the raw text ourselves and determining what features may be important, 
            and not have the data preproccesed or turned into vectors.
            Next we wanted data that was conversational, that didn't use too much 
            slang or leetspeak and was in general proper English. The size of the
            dataset needed to be fairly large, at least 1000, for frequency analysis.
             Lastly, we would like a dataset that was referenced in multiple papers to make comparisons
            of our results to others. So we shortlisted a few datasets that fulfilled
            some of these characteristics.

            The UCI SMS Spam Dataset is a collection of conversational text messages
            origninating from a variety of sources.

            TODO: needed info?

@@

            TODO: methodology

@@

            Now data was stored in memory as Python objects for processing through the
            feature extractor.

@@

        %\section{Classifier Selection}

        %\section{Classifier Tuning}

        %\section{Results}

        %\section{Evaluation}

>>>>

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{sectsty}
\usepackage{multicol, caption}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subfig}
%\usepackage{subcaption}

%\usepackage{biblatex}
\usepackage[margin=0.5in]{geometry} % don't know what size margins to use
\newenvironment{Figure}
  {\par\medskip\noindent\minipage{\linewidth}}
  {\endminipage\par\medskip}

@@

            In this paper we explore the selection public datasets, data preparation,
            feature extraction and finally the selection and tuning of classifiers.
            We will do this following the process illustrated in Figure \ref{fig:process}.
        \section{Dataset Selection}
            The correct selection of a dataset was crucial to the testing of 
            different types of features. There were many characteristics that were
            on our `wishlist.' Such as having the freedom of processing 
            the raw text ourselves and determining what features may be important, 
            and not have the data preproccesed or turned into vectors.
            Next we wanted data that was conversational, that didn't use too much 
            slang or leetspeak and was in general proper English. The size of the
            dataset needed to be fairly large, at least 1000, for frequency analysis.
            Lastly, we would like a dataset that was referenced in multiple papers to make comparisons
            of our results to others.

            So we shortlisted a few datasets that fulfilled some of these characteristics, but
            settled on the SpamAssasin Dataset which fulfilled all of our requirements
            with raw email data that mostly consisted of both business and casual
            conversations. It consisted of both easy and hard data, but we stuck with
            just the easy data as many of the hard pieces of data were too difficult
            to classify without more information about the user.

@@

            With so much metadata given with this dataset, we wanted to take advantage
            of it for use as potential features. In preprocessing we found many features
            that could signature of spam emails such as excessive links or attachments.
            The processes illustrated with Figure \ref{fig:preprocess}, is an overview
            of the processes that will be preformed in this step.

            \begin{Figure}
                \centering
                \includegraphics[width=\linewidth]{figures/prep.png}
                \captionof{figure}{Preparation Process}
                \label{fig:preprocess}
            \end{Figure}

@@

            Now data was stored in memory as Python objects for processing through the
            feature extractor. We shuffled and then split the data 
            80:20 into a training and testing set respectively.

@@

            The next step is to extract the necessary features and then vectorize
            them for training with our classifier. The first step of extraction was
            to

            \begin{minipage}{0.4\columnwidth}
                \includegraphics[width=\textwidth]{figures/spam_wc}
                \captionof{figure}{Spam}
                \label{spam_wc}
            \end{minipage}
            \begin{minipage}{0.4\columnwidth}
                \includegraphics[width=\textwidth]{figures/ham_wc}
                \captionof{figure}{Ham}
                \label{ham_wc}
             \end{minipage}
            This is more text
        %\section{Classifier Selection}

        %\section{Classifier Tuning}
            % Grid Search and Cross Validation
            % play with Max amount of features to see if have effect
        %\section{Results}
            % important metrics, why
        %\section{Evaluation}
